---
title: "CREDI Multi-dimensional Item Factor Analysis Scoring"
author: "Jonathan Seiden"
date: "7/15/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The [Caregiver Reported Early Development Instruments](https://credi.gse.harvard.edu/) is a measure of early development that is administered through an interview or survey completion by a child's parent or primary caregiver. This program is designed to process the raw response data to calculate scores. 

This package produces several scores based on input data, and supports both data collected on the Long Form and Short Form versions of CREDI.  Most users will prefer to use the [online scoring app](https://credi.shinyapps.io/Scoring_App) which does not require the use of R in order to calculate scores, but this package is made publically available to advanced users and those  who wish to understand the multi-dimensional factor analysis process used to calculate overal and domain-level scores.  

See the [CREDI scoring manual](https://projects.iq.harvard.edu/files/credi/files/credi-scoring-manual-8-jun-20181.pdf) for more details about score calculation.

## Installation

Installing the CREDI scoring app is currently only available through GitHub. Easily download and install with the below lines of code:  


```{r install, eval = FALSE}
require(devtools)
devtools::install_github("https://github.com/marcus-waldman/credi")
```

## Example

Most users will only use the `score` function, which converts raw item responses into overall, short-form, domain, and normalized reference scores. All other functions included in the `credi` package are called by this function. These other functions are exported provided for reference, explanation, and clarity, but are not designed for standalone use. 

Below is a very simple example with three simulated children, each of whom only had 5 Long Form questions. Note that one child is missing a value for LF1, resulting in no score being calculated for the child because the `min_items` parameter was set to 5. 

```{r example, warning=FALSE, message=FALSE}
library(credi)

#Create a sample dataframe
dat <- data.frame(
  ID = 1:3,
  AGE = c(3, 5, 4),
  LF1 = c(1, 0, NA),
  LF2 = c(0, 0, 0),
  LF3 = c(1, 0, 1),
  LF4 = c(1, 1, 1),
  LF5 = c(1, 0, 0)
)

#Score the dataframe
scored_dat <- credi::score(
  data = dat,
  reverse_code = FALSE,
  interactive = FALSE,
  min_items = 5
)

#Print out domain scores:
scored_dat$scores[, c("SF", "MOT", "LANG", "SEM", "COG", "OVERALL")]

```
